Cross-validation of regression models: mixed model examples (edited v3)

### 2024-07-24 scratch/JSS-submission/Fox-Monette-cv-package.Rmd
adjust size of C+R plots to save 1 page

```{r Auto-explore-cr-plots}
#| out.width = "95%",
#| fig.height = 5.5,
#| fig.align = 'center',
#| fig.cap = "Component + residual plots for the working model fit to the \\code{Auto} data."
m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, pch = ".", ylab = "C+R", las = 2)
```

@@

```{r Auto-transformed-cr-plots}
#| out.width = "95%",
#| fig.align = 'center',
#| fig.height = 5.5,
#| fig.cap = "Component + residual plots for the regression model fit to the transformed \\code{Auto} data."
crPlots(m, pch = ".", ylab = "C+R", las = 2)
```

>>>>

```{r Auto-explore-cr-plots}
#| out.width = "70%",
#| fig.height = 4.25,
#| fig.align = 'center',
#| fig.cap = "Component + residual plots for the numeric predictors in the working model fit to the \\code{Auto} data."
m.auto <- lm(mpg ~ ., data = Auto)
crPlots(m.auto, 
        terms = ~ displacement + horsepower + weight + acceleration, 
        pch = ".", ylab = "C+R", las = 2)
```

@@

```{r Auto-transformed-cr-plots}
#| out.width = "70%",
#| fig.align = 'center',
#| fig.height = 4.25,
#| fig.cap = "Component + residual plots for the regression model fit to the transformed \\code{Auto} data."
crPlots(m, terms = ~ displacement + horsepower + weight + acceleration, 
        pch = ".", ylab = "C+R", las = 2)
```
